---
title: "Activity: Street or Road?"
author: "Willem Krantz"
output: html_notebook
---

## Load in the data

```{r}
#load libraries 
library(tidyverse)
library(dcData)
library(esquisse)
#load in the data here 
# we will only be using the "street-addresses.csv" file from the text



  


```

## Recreate Solved Example using `sample(50)`

```{r}
Addresses<-read_csv("https://mdbeckman.github.io/dcSupplement/data/street-addresses.csv")
Sample<-
  Addresses%>%
  sample_n(size=50)

Matches<-
  Sample%>%
  filter(grepl(pattern= "PO", address))
```

## Recreate Soved Example using the entire `Address` data set

```{r}
Dont<-
  Sample%>%
  filter(!grepl(pattern="PO",address))

```

#### Additional Question: How many addresses are a PO BOX (including NCSU BOX)? 

```{r}
Sample%>%
   filter(grepl(pattern= "PO", address))%>%
  summarise(count=n())


```

My answer here...... 

33
## Back to the Streets: Your Turn

#### Part 1: Explain (in english) each line of the following code chunk

```{r}
pattern <- "(ST|RD|ROAD)"
LeftOvers <-
  Addresses %>% 
  filter( !grepl(pattern, address),
          !grepl("\\sAPT|UNIT\\s[\\d]+$", address),
          !grepl(" BOX ", address)
          )
```

My answer here.......
line one names the new table 
line 2 defines it as leftovers 
line 3 pulls from our addresses 
line 4 filters by pattern specifically apartment, unit, po box and address. 



#### Part 2: Implement your method on the entire `Addresses` data set. Explain how your code works line by line.

```{r}



```

My answer here.......

#### Additional Question 1: Present your result from part 2 by providing a table in descending order of popularity for the street name endings you found

```{r}


```

#### Additional Question 2: Present your result by using ggplot to a bar chart in descending order of popularity for the street name endings you found previously.

Note: make sure your order street names according to popularity, not alphabetically.

```{r}

```

#### Additional Question 3: Comment on any patterns you see

My answer here.......
